Technical Report

### 2018-01-19 fully-abstract-comp/technical-report.tex
A quick and dirty write-up of possible new future world relation.

\subsection{Future world}
For both $\privft$ and $\pubft$ we have
\begin{mathpar}
  \inferrule{ \exists m : \RegionName \fun \RegionName, \text{ injective}\ldotp \dom(W') \supseteq \dom(m(W)) \wedge \forall r \in \dom(W)\ldotp W'(m(r)) \future W(r) }
            { W' \future W }
\end{mathpar}
%
The private future regions allow transitions in the private part of the transition system. They also allow $\spatial$ regions to become $\revoked$:
\begin{mathpar}
  \inferrule{ }
  { \revoked \privft (\spatial,\_,\_,\_,\_)}
\and
  \inferrule{ }
            { \revoked \privft \revoked }
\and
  \inferrule{ (s,s') \in \phi }
            { (v,s',\phi_\pub,\phi,H) \privft (v,s,\phi_\pub,\phi,H)  }
\end{mathpar}
%
Public future regions are allowed to transition according to the public part of their transition system.
\begin{mathpar}
    \inferrule{ }
            { \revoked \pubft \revoked }
\and
  \inferrule{ (s,s') \in \phi_\pub }
            { (v,s',\phi_\pub,\phi,H) \pubft (v,s,\phi_\pub,\phi,H)  }
\end{mathpar}

>>>>

\subsection{Future world}
\subsubsection{\color{green} first thoughts on change to future world relation}
{\color{green}
The public part of the future world relation stays the same:
\begin{mathpar}
  \inferrule{ \exists m : \RegionName \fun \RegionName, \text{ injective}\ldotp \dom(W') \supseteq \dom(m(W)) \wedge \forall r \in \dom(W)\ldotp W'(m(r)) \pubft W(r) }
            { W' \future W }
\end{mathpar}
The private future world relation becomes:
\begin{mathpar}
  \inferrule{ \exists m : \RegionName \fun \RegionName, \text{ injective}\ldotp \dom(W') \supseteq \dom(m(W)) \wedge \forall r \in \dom(W)\ldotp W'(m(r)) \privft W(r) \\  \exists r \in \dom(W') \cap \dom(W)\ldotp W'(r) \text{ is non-empty and stack region}}
            { W' \future W }
\end{mathpar}
where we take "is non-empty and stack region" to mean the following:

\begin{definition}
  We say a region $(k,s,\phi_\pub,\phi,H)$ is non-empty iff
\[
  \begin{array}{l}
    \forall n, \hat{W},s'\ldotp \forall \npair{\stpair{\ms}{\ms}} \in H \; s' \; \hat{W} \ldotp \dom(\src{\ms_S}) > 0 \wedge \dom(\ms_T) > 0 
  \end{array}
\]
\end{definition}

\begin{definition}
  We say a region $(k,s,\phi_\pub,\phi,H)$ is a stack region on a machine with starting stack domain $[\stkb,\eaddr]$ iff
\[
  \begin{array}{l}
    \forall n, \hat{W},s'\ldotp \forall \npair{\stpair{\ms}{\ms}} \in H \; s' \; \hat{W} \ldotp \dom(\src{\ms_S}) \subset [\stkb,\eaddr]  \wedge \dom(\ms_T) \subset [\stkb,\eaddr]
  \end{array}
\]
\end{definition}

}

For both $\privft$ and $\pubft$ we have
\begin{mathpar}
  \inferrule{ \exists m : \RegionName \fun \RegionName, \text{ injective}\ldotp \dom(W') \supseteq \dom(m(W)) \wedge \forall r \in \dom(W)\ldotp W'(m(r)) \future W(r) }
            { W' \future W }
\end{mathpar}
%
The private future regions allow transitions in the private part of the transition system. They also allow $\spatial$ regions to become $\revoked$:
\begin{mathpar}
  \inferrule{ }
  { \revoked \privft (\spatial,\_,\_,\_,\_)}
\and
  \inferrule{ }
            { \revoked \privft \revoked }
\and
  \inferrule{ (s,s') \in \phi }
            { (v,s',\phi_\pub,\phi,H) \privft (v,s,\phi_\pub,\phi,H)  }
\end{mathpar}
%
Public future regions are allowed to transition according to the public part of their transition system.
\begin{mathpar}
    \inferrule{ }
            { \revoked \pubft \revoked }
\and
  \inferrule{ (s,s') \in \phi_\pub }
            { (v,s',\phi_\pub,\phi,H) \pubft (v,s,\phi_\pub,\phi,H)  }
\end{mathpar}
